---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Title and Package description

## Title

**ovsa**: (ordinal variable sensitivity analysis)

## Description

The goal of *ovsa* package is to perform sensitivity analysis for ordinal variable  when specific catégories of ordinal variable tend to be missing
(Missing Not At Random).

Our sensitivity analysis containes three step

1. Performing MI under MAR

2. Modifying the imputed data to reflect plausible scenarios under MNAR

3. Analyzing the modified data and combining the results according to Rubin’s rule.

<!-- badges: start -->
<!-- badges: end -->

The goal of ovsa is to ...

## Installation

You can install the development version of ovsa from [GitHub](https://github.com/) with:

```
# install.packages("pak")
pak::pak("abdoulaye-dioni/ovsa")
```

```
# install.packages("devtools")  # Uncomment if you don't have devtools installed
devtools::install_github("abdoulaye-dioni/ovsa")
```



## Example


```{r example}
library(ovsa)
```

Below is a minimal working example demonstrating the usage of the ovsa package.

```{r}
head(simdaNA)
str(simdaNA)
imputed_mice <- firststep(simdaNA[, c("Y","X1.mis","X2")], mi = "mice",
method = c("logreg", "polr", "polyreg"), m = 10,printFlag = FALSE)
library(mice)

summary(complete(imputed_mice,1))
#Formula for ordinal regression
formula <- "X1.mis.mar ~ Y + X2"
manydelta <- data.frame( delta1 = c(0,0,0,0), delta2 = c(0,-1,2,0),
delta3 = c(0,0.5,0,0.5), delta4 = c(-1,0.5,0,1))
level_ord_var = 5
seed = 123
# Execution of the complete function
 out <- secondstep( data = simdaNA, mardata = imputed_mice,
level_ord_var = level_ord_var, formula = formula, manydelta = manydelta,
seed = seed)
summary(out$mnardata[[2]])
```

