---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# **ovsa**: ordinal variable sensitivity analysis


## Description

## Description
The goal of the ovsa package is to perform sensitivity analysis for ordinal variables when specific categories are prone to missingness under a Missing Not At Random (MNAR) mechanism.

1. Our sensitivity analysis procedure involves three main steps:

2. Performing multiple imputation (MI) under the MAR assumption and

Modifying the imputed values to reflect plausible MNAR scenarios

3. Analyzing the modified datasets and combining the results using Rubin’s rules



# Installation

You can install the development version of ovsa from GitHub using either ***pak*

or **devtools**  

```{r,eval=FALSE}
# install.packages("pak")
pak::pak("abdoulaye-dioni/ovsa")
```


```{r,eval=FALSE}
# install.packages("devtools")
devtools::install_github("abdoulaye-dioni/ovsa")
```




# Example

Below is a simple workflow illustrating the main steps of the ovsa package for

non hierarchical data.

```{r example}
library(ovsa)
```


## Non hierarchical data from the `ovsa` package

```{r}
data("simda") 
head(simda)
```



## Simulating MNAR with **simmnar()**

Use the simmnar() function to simulate a Missing Not At Random (MNAR) mechanism for ordinal variables:

```{r}
set.seed(321)
simdaNA <- simmnar(data = simda, Y = "Y",
                   ord_var = "X1", A = 2, probA = 0.5,
                   B = 4, probB = 0.8, verbose = TRUE)
head(simdaNA)
summary(simdaNA)
str(simdaNA)
```



## Step 1: Imputation under MAR with `firststep()`

Use the `firststep` function from the `ovsa` package to impute missing values in a non-hierarchical context. This function performs the first step of our sensitivity analysis for ordinal variables under a Missing Not At Random (MNAR) mechanism.

```{r}
library(mice)
imputed_mice <- firststep(simdaNA[, c("Y", "X1.mis", "X2")],
                          mi = "mice",
                          method = c("logreg", "polr", "polyreg"),
                          m = 10,
                          printFlag = FALSE,verbose = FALSE)

summary(complete(imputed_mice, 1))
```


```{r}
summary(complete(imputed_mice,1))
```


## Step 2: Modify imputed values with `secondstep()`



```{r}
formula <- "X1.mis.mar ~ Y + X2"
manydelta <- data.frame(
  delta1 = c(0, 0, 0, 0),
  delta2 = c(0, -1, 2, 0),
  delta3 = c(0, 0.5, 0, 0.5),
  delta4 = c(-1, 0.5, 0, 1)
)

level_ord_var <- 5
seed <- 123
```

```{r}
out <- secondstep_mice(data = simdaNA, mardata = imputed_mice,
                  level_ord_var = level_ord_var,
                  formula = formula,
                  manydelta = manydelta,
                  seed = seed)

summary(out$mnardata[[2]])
```

```{r}
summary(out$mnardata[[2]])
```


##  Check plausibility with `checkprop()`


```{r}
checkprop(data = out$mnardata,
          ord_mar = "X1.mis.mar",
          ord_mis = "X1.mis",
          manydelta = manydelta)
```


## Step 4: Final analysis with `thirdstep()`

```{r}
formula <- "Y ~ X1.mis.mar + X2"

# Analysis for MAR
thirdstep_mice(data = out$mnardata, formula = formula)

# Analysis for MNAR
thirdstep_mice(data = out$mnardata, manydelta = manydelta)
```

